`tidyfun`

### 2019-06-11 tidyfun.Rmd
some post-conference tweaks to tidyfun talk

This page hosts a presentation / quick intro to `tidyfun` -- enjoy!

@@

The `tidyfun::dti_df` contains ractional anisotropy (FA) tract profiles for the corpus callosum (cca) and the right corticospinal tract (rcst), along with several covariates.

@@

**`tf`** is a new data type for (vectors of) functional data:

- an abstract superclass for functional data in 2 forms:
    - as (argument, value)-tuples: subclass **`tfd`**, also irregular or sparse
    - or in basis representation: subclass **`tfb`**

- Includes additional attributes that define *function-like* behavior:
    - how to **evaluate** the given "functions" for new arguments
    - their **domain** 
    - the **resolution** of the argument values

First I'll pull a `tf` vector from the `tidyfun::dti_df` dataset, and then I'll extract a simple 5-element vector of functions interpolated to be on a regular grid. The resulting vector contain fractional anisotropy tract profiles for the corpus callosum (`cca`). When printed, `tf` vectors show the first few `arg` and `value` pairs for each subject.

@@

cca_five = dti_df$cca[1:5]
cca_five = tfd(cca_five, arg = seq(0, 1, l = 93), interpolate = TRUE)

cca_five
```

@@

Functional data in basis representation:

- represented as a list of **`coefficients`** and a common **`basis_matrix`** of basis function evaluations on a vector of `arg`-values.
- contains a **`basis`** function that defines how to compute the basis for new **`arg`**s and how to differentiate or integrate it.
- (internal) flavors: 
    - `tfb_spline`: uses `mgcv`-spline bases 
    - `tfb_fpc`: uses functional principal components

It's possible to convert between types.

@@

You can smooth data using `tf_smooth`; this differs from converting to subclass `tfb`:

```{r}
cca_five_smooth = 
  cca_five %>% 
  tf_smooth("lowess")

plot(cca_five)
lines(cca_five_smooth, col = "blue")
```

@@

Integration with analysis is longer-term goal

>>>>

This page hosts a presentation / quick intro to [`tidyfun`](https://fabian-s.github.io/tidyfun/) -- enjoy!

@@

The `tidyfun::dti_df` contains fractional anisotropy (FA) tract profiles for the corpus callosum (cca) and the right corticospinal tract (rcst), along with several covariates.

@@

**`tf`** is a new data type for (vectors of) functional data. It contains subclasses for "raw" functional data (`tfd`) that can be dense / sparse and regular / irregular, and for "basis representation" functional data (`tfb`). Internally, there are attributes that define *function-like* behavior, including evaluation for new arguments, resolution, and the functional domain.

First I'll pull a `tf` vector from the `tidyfun::dti_df` dataset. The resulting vector contain fractional anisotropy tract profiles for the corpus callosum (`cca`). When printed, `tf` vectors show the first few `arg` and `value` pairs for each subject.

@@

cca_five = dti_df$cca[1:5]
cca_five
```

@@

Converting "raw" to "basis" representation is possible, and introduces some smoothing by default.

@@

@@

Integration with analysis is longer-term goal:
